% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2018 Jonathan Nicholas <Jonathan.Nicholas@protonmail.com> http://chromadream.github.io
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{5pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{{\Large Jonathan Nicholas}}\\
\texttt{Jonathan.Nicholas@protonmail.com} & \texttt{chromadream.github.io} \\
\texttt{https://github.com/Chromadream}

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Monash University}{Melbourne, AU}{B.InfoTech (Computer Network \& Security)}{2017 - 2018}
	\begin{itemize}
		\resitem{GPA 3.5 (7.9/10)}
		\resitem{Participated in UniHack Mini Monash, 2017}
		\resitem{Developed two major software development project on PHP 7 as main developer}
	\end{itemize}

\item
	\ressubheading{Monash University}{Melbourne, AU}{Diploma of Engineering (IT Stream)}{2016 - 2017}
	\begin{itemize}
    \resitem{GPA 3.75 (8.3/10)}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{GlobalX}{Melbourne, AU}{Software Developer}{Jan 2019 - present}
	\begin{itemize}
	  \resitem{Maintained a large-scale workflow productivity tool for conveyancers in Australia}
	  \resitem{Maintained a legacy tool that is used by the company to integrate with other companies}
	  \resitem{Part of a project to improve document storage and workflow}
	  \resitem{Build, maintain, and improve CI/CD pipeline used throughout the company}
	\end{itemize}

\item
	\ressubheading{Oilee Racing}{Melbourne, AU}{Full-stack Developer}{Feb 2018 - Nov 2018}
	\begin{itemize}
		\resitem{Developed an internal company management suite which has features such as \textbf{job tracking}, \textbf{invoicing}, and \textbf{notetaking} at company level.}
		\resitem{Improved the business process significantly by reducing the reliance for the owner's phone for job tracking.}
		\resitem{Developed the system in LAMP stack with CakePHP on the backend, and Vue.js on the frontend.}
	\end{itemize}

\item
	\ressubheading{Gemilang Photocopy}{Jakarta, Indonesia}{Full-stack Developer}{Nov 2016 - Jun 2018}
	\begin{itemize}
		\resitem{Developed a complete internal system for a printing company in Indonesia which has features such as \textbf{point-of-sales}, \textbf{inventory control}, among many other features.}
		\resitem{Improved the business significantly by improving the accountability of the company and reducing the reliance for the owner of the company to do day-to-day operations.}
		\resitem{Developed the system in LAMP stack on the backend, and Vanilla JS on the frontend.}
	\end{itemize}

\end{itemize}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Technical Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Programming Languages:} Python 3, C\#, Ruby, Java, SQL family, Node.js, JavaScript, and TypeScript.
\item {\bf Frameworks and Libraries:} Angular 2+, ASP.NET Core, Entity Framework, Vue.js, Flask.
\item {\bf Development Tools:} git, Visual Studio Code, TeamCity, Octopus Deploy, Docker, Kubernetes, Google Cloud Platform.
\item {\bf Development Practices:} TDD, Agile Development, Scrum, Continuous Integration/Continous Delivery (CI/CD).
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Awards and Scholarship}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Monash University's Information Technology International Merit Scholarship (2017):} A scholarship awarded from Monash University for exceptional study progression and results.
\item {\bf Monash College's Academic Excellence Award (2016):} Awarded for “Introduction to Algorithms and Programming”.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Volunteering Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Monash Student Union Volunteer}{Melbourne, AU}{Library Volunteer}{Feb 2018 - Nov 2018}
	\begin{itemize}
			\resitem{Worked in team to ensure that the Monash Student Union’s library collections are preserved correctly and neatly.}
\end{itemize}

\item
	\ressubheading{Monash University}{Melbourne, AU}{Peer Mentor}{Feb 2018 - Jun 2018}
	\begin{itemize}
			\resitem{Provided guidance to first year students of Monash University.}
\end{itemize}

\item
	\ressubheading{Monash College}{Melbourne, AU}{IT Student Ambassador}{Oct 2016 - Feb 2017}
	\begin{itemize}
			\resitem{Provided technical guidance to newly-enrolled Monash College students.}
			\resitem{Received positive feedbacks from fellow ambassadors and clients.}
\end{itemize}

\end{itemize}

\end{document}
